A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/02_Materials_and_Methods.Rmd
added subsections

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database. The classes of the variable \textit{burial type} are distinguished by colour, the ones of \textit{burial construction} by shape. The red frame indicates the research area. The Map projection is EPSG:102013 and the base layer (land, rivers, lakes) data is taken from the Natural Earth project (\url{www.naturalearthdata.com}).}
\end{figure}

The analysis code of this paper is written in the statistical programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible. A more in-depth description and discussion of the data preparation steps can be found in the master thesis this article is based on [@schmidComputerbasiertesCulturalEvolution2018].

@@

@@

@@

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean squared euclidian distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database (\url{radon-b.ufg.uni-kiel.de}). The classes of the variable \textit{burial type} are distinguished by colour, the ones of \textit{burial construction} by shape. The red frame indicates the research area. The Map projection is EPSG:102013 and the base layer (land, rivers, lakes) data is taken from the Natural Earth project (\url{www.naturalearthdata.com}).}
\end{figure}

The code of this paper is written in the statistical programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible. A more in-depth description and discussion of the data preparation steps can be found in the master thesis this article is based on [@schmidComputerbasiertesCulturalEvolution2018].

## Data

@@

## Data preparation

@@

## Time series

@@

## Cultural distance

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean squared euclidian distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other. Negative correlation coefficients are printed red and $p$-values below $0.1$ bold.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

### 2019-01-13 article/03_Results.Rmd
added subsections

Figure \ref{development_burial_type} and \ref{development_burial_construction} show the region-wise time series of trait occurrence. If we ignore all other archaeological knowledge, we can construct the following narrative from them:

@@

This narrative is wrong in many aspects. The following section contains a short comparison with the archaeological state of research for each region:

>>>>

## Timeseries

Figure \ref{development_burial_type} and \ref{development_burial_construction} show the region-wise time series of trait occurrence. If we ignore all other archaeological knowledge, we can construct the following narrative from them.

@@

This narrative is wrong in many aspects. The following section contains a short comparison with the archaeological state of research for each region.
